Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
paper: combine graphs and captions
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[h]
\centering
\includegraphics[width=75mm,trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit.}
\label{fig:propdelay}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-performance.png}
\includegraphics{figures/mantle-balancer-performance.png}
\caption{All CephFS balancing modes have the same performance Mantle uses a
balancer designed for sequencers.}\label{fig:mantle-balancer-performance}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=60mm,trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit.}
\label{fig:propdelay}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-performance.png}
\includegraphics{figures/mantle-mode-performance.png}
\caption{In (a) all CephFS balancing modes have the same performance; Mantle uses a
balancer designed for sequencers. In (b) the best combination of mode and
migration units can have up to a 2\(\times\) improvement.}\label{fig:mantle-balancer-performance}
\end{figure}
